Linked Open Social Data for Scientific Benchmarking (Supporting Information document)

### 2016-07-26 supportingInformation.tex
added starting version of supporting information

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{changepage}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{pdfpages}
\usepackage{incgraph,tikz}
% \usepackage[showframe=true]{geometry}
%
\newcommand{\textttt}[1] {\texttt{\footnotesize#1}}
\newcommand{\h} {\hphantom ~ }
% \newcommand{\textttt}[1] {\mbox{\texttt{\footnotesize#1}}}
% \newcommand{\textttt}[1] {
% \begin{verbatim} #1 \end{verbatim}
% }
\pgfplotsset{compat=1.5}
\pgfplotsset
{
	width=0.5\textwidth,
	x tick label style={/pgf/number format/1000 sep=},
  enlarge x limits = 0.0,
  ymajorgrids=true,
	major tick style={draw=none},
  ymin = 0.0,
	every axis/.append style={
		every x tick label/.append style={font=\tiny},
    every y tick label/.append style={font=\tiny},
    every axis label/.append style={font=\small},
    height=37mm,
    width=37mm,
    title style={at={(0.5,0.90)}, font=\normalfont},
    xticklabel style={yshift=4pt}
	}
}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother
\begin{document}
%
\begin{frontmatter}
%
\title{Linked Open Social Data for Scientific Benchmarking}
%
\author[pwr]{Renato Fabbri\corref{corresponding}\fnref{kio-url}}
\ead{fabbri@usp.br}
%
\author[pwr]{Osvaldo Novais de Oliveira Junior\fnref{kio-url}}
\ead{chu@ifsc.usp.br}
%
\cortext[corresponding]{Corresponding author}
\address[pwr]{S\~ao Carlos Institute of Physics, S\~ao Paulo
University, Brazil}
%
\fntext[kio-url]{\textit{URL:} \url{http://www.ifsc.usp.br/}}
%
\begin{abstract}
\end{abstract}
%
\begin{keyword}
Big Data, Data Mining, Benchmark Data, Facebook, Twitter, IRC, Email, Complex Networks
%Hierarchy of Clusters \sep HoC \sep Benchmark Dataset \sep Benchmark Data Generator \sep Artificial Data \sep Cluster Analysis \sep Tree Structured Stick Breaking Process \sep TSSB \sep ...
\end{keyword}

\end{frontmatter}
\pdfpageheight 6in
\section{Introduction}
% \includepdf{ontologies/aairc.ttl/draw.pdf}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Paper sized to picture};}
    paper=graphics
    ]{ontologies/aairc.ttl/draw.png}

\section{Conclusions}
\label{conclusions}
\pdfpageheight 2in
The Linked Open Social Data (LOSD) presented in this article
should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
One should access \url{http://wiki.nosdigitais.teia.org.br/LOSD}
for reaching the address where LOSD is currently reachable.

>>>>

\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black},
    pdfborder={0 0 0}
}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
% \usepackage{changepage}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{pdfpages}
\usepackage{incgraph,tikz}
\usepackage[titles]{tocloft}
\setlength{\cftbeforesecskip}{-.5ex}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% \usepackage[showframe=true]{geometry}
%
\newcommand{\textttt}[1] {\texttt{\footnotesize#1}}
\newcommand{\h} {\hphantom ~ }
% \newcommand{\textttt}[1] {\mbox{\texttt{\footnotesize#1}}}
% \newcommand{\textttt}[1] {
% \begin{verbatim} #1 \end{verbatim}
% }
\pgfplotsset{compat=1.5}
\pgfplotsset
{
	width=0.5\textwidth,
	x tick label style={/pgf/number format/1000 sep=},
  enlarge x limits = 0.0,
  ymajorgrids=true,
	major tick style={draw=none},
  ymin = 0.0,
	every axis/.append style={
		every x tick label/.append style={font=\tiny},
    every y tick label/.append style={font=\tiny},
    every axis label/.append style={font=\small},
    height=37mm,
    width=37mm,
    title style={at={(0.5,0.90)}, font=\normalfont},
    xticklabel style={yshift=4pt}
	}
}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%
\makeatletter
\def\ps@pprintTitle{%
    \let\@oddhead\@empty
    \let\@evenhead\@empty
    \def\@oddfoot{}%
\let\@evenfoot\@oddfoot}
\makeatother
\begin{document}
%
\begin{frontmatter}
%
\title{Linked Open Social Data for Scientific Benchmarking (Supporting
Information document)}
%
\author[pwr]{Renato Fabbri\corref{corresponding}\fnref{kio-url}}
\ead{fabbri@usp.br}
%
\author[pwr]{Osvaldo Novais de Oliveira Junior\fnref{kio-url}}
\ead{chu@ifsc.usp.br}
%
\cortext[corresponding]{Corresponding author}
\address[pwr]{S\~ao Carlos Institute of Physics, S\~ao Paulo
University, Brazil}
%
\fntext[kio-url]{\textit{URL:} \url{http://www.ifsc.usp.br/}}
%
\begin{abstract}
This is a Supporting Information document which exposes ontological
diagrams and auxiliary tables for the Linked Open Social Data (LOSD)
database. The main article is in~\cite{losd}.
\end{abstract}
%
\begin{keyword}
Big Data, Data Mining, Benchmark Data, Facebook, Twitter, IRC, Email, Complex Networks
%Hierarchy of Clusters \sep HoC \sep Benchmark Dataset \sep Benchmark Data Generator \sep Artificial Data \sep Cluster Analysis \sep Tree Structured Stick Breaking Process \sep TSSB \sep ...
\end{keyword}

\end{frontmatter}
\pdfpageheight 8in
\tableofcontents
\section{General guidance}
In this document we provide diagrams
the provenances in the LOSD:
Facebook, Twitter, IRC, Email, ParticipaBR, Cidade Democrática and AA.
Each provenance diagram was broken in two, one present the relations
among main classes and datatypes, the other present metadata on the
snapshot.

Furthermore, this document ends with two sets of tables, one with countings of
triples, participants, edges/interactions/relations and characters,
the other with references for snapshot groups, such as wikipedia or
contact links.

\section{Facebook data}

% \includepdf{ontologies/aairc.ttl/draw.pdf}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Facebook};}
    paper=graphics
][scale=.6]{ontologies/facebook-legacy-Auricultura10042013Friendship.ttl/draw.png}

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Facebook};}
    paper=graphics
][scale=.5]{ontologies/facebook-legacy-Auricultura10042013Meta.ttl/draw.png}

\section{Twitter data}
\pdfpageheight 4in
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  Twitter };}
    paper=graphics
][scale=.5]{ontologies/twitter-legacy-arenaNETmundialTweet00000.ttl/draw.png}

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Twitter};}
    paper=graphics
][scale=.5]{ontologies/twitter-legacy-arenaNETmundialMeta.ttl/draw.png}

\section{IRC data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge IRC};}
    paper=graphics
][scale=.7]{ontologies/irc-legacy-hackerspace-cpsLog00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge IRC};}
    paper=graphics
][scale=.6]{ontologies/irc-legacy-hackerspace-cpsMeta.ttl/draw.png}

\section{Email data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.4]{ontologies/gmane-legacy-.linux.audio.devel1-20000Email00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Email};}
    paper=graphics
][scale=.5]{ontologies/gmane-legacy-.linux.audio.devel1-20000Meta.ttl/draw.png}

\section{ParticipaBR data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  ParticipaBR};}
    paper=graphics
][scale=.5]{ontologies/participabr.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  ParticipaBR};}
    paper=graphics
][scale=.7]{ontologies/participabr.ttl/draw_circo.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge
  ParticipaBR};}
    paper=graphics
][scale=.7]{ontologies/participabrMeta.ttl/draw.png}

\section{Cidade Democrática data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.4]{ontologies/cidadedemocratica00000.ttl/draw_circo.png}

\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge Cidade
  Democrática};}
    paper=graphics
][scale=.7]{ontologies/cidadedemocraticaMeta.ttl/draw.png}
\section{AA data}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.6]{ontologies/aairc.ttl/draw.png}
\incgraph[
  overlay={\node[red,below right] at (page.north west) {\Huge AA};}
    paper=graphics
][scale=.7]{ontologies/aaircMeta.ttl/draw.png}

\section{Snapshot references}
\label{sreferences}
\pdfpageheight 10in
\section{Elementary counting in snapshots}
